\documentclass{beamer}

\usepackage[utf8]{inputenc}

\title[About Beamer] %optional
{Metodologie e algoritmi per la calibrazione di centraline dedicate al monitoraggio della qualità dell'aria}
\usetheme{Copenhagen}
\subtitle{A short story}

\author{Edoardo D'Angelis\\[3mm]Prof. Andrew D. Bagdanov, Prof P. Pala\\[3mm]Walter Nunziati\\[3mm]Alice Cavaliere}

\institute[UNIFI] % (optional)
{
  Università degli studi di Firenze\\
  Dipartimento di Ingegneria
}

\date{}

\begin{document}

\frame{\titlepage}

\begin{frame}
\frametitle{Sample frame title}
This is a text in second frame. 
For the sake of showing an example.

\begin{itemize}
 \item<1-> Text visible on slide 1
 \item<2-> Text visible on slide 2
 \item<3-> Text visible on slide 3
 \item<4-> Text visible on slide 4
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Sample frame title}

In this slide, some important text will be
\alert{highlighted} because it's important.
Please, don't abuse it.

\begin{block}{Remark}
Sample text
\end{block}

\begin{alertblock}{Important theorem}
Sample text in red box
\end{alertblock}

\begin{examples}
Sample text in green box. The title of the block is ``Examples".
\end{examples}
\end{frame}

\begin{frame}
\frametitle{Two-column slide}
\begin{columns}
\column{0.5\textwidth}
This is a text in first column.
$$E=mc^2$$
\begin{itemize}
\item First item
\item Second item
\end{itemize}

\column{0.5\textwidth}
This text will be in the second column
and on a second thoughts, this is a nice looking
layout in some cases.
\end{columns}
\end{frame}

\end{document}
